---
title:  Hello cruel world
output:
  litedown::html_format:
    meta:
      css: "../_liteblog.css"
    options:
      toc: true
      js_highlight:
        package: prism
        style: tomorrow
---

```{r}
#| label: setup
#| echo: false
.blog <- readRDS("../_liteblog.rds")
```

It is traditional, when tinkering with a new blogging tool that you just made and will almost certainly abandon within a week, to write a "hello world" style post that serves as a quick check that the tool is working. This tradition almost certainly developed because nobody bothers to write unit tests for code that isn't supposed to be used in the wild. This blog is no exception. 

## Markdown

### Lists

Unnumbered lists, with nesting.

- blah blah blah
    - blah blah
    - blah
- blah blah blah
- blah blah

Numbered lists, also with nesting.

1. blah blah blah
    1. blah blah
    2. blah
2. blah blah blah
3. blah blah

### Font

Markdown syntax for *italics* is supported, as is **boldface**, and ~strikethrough~.

### Tables

State       |Code  |Capital   |Population
------------|-----:|---------:|---------:
New South Wales|NSW|Sydney|8,484,357 	
Victoria|VIC|Melbourne|6,981,352
Queensland|QLD|Brisbane|5,586,322
Western Australia|WA|Perth|2,965,159
South Australia|SA|Adelaide|1,878,029
Tasmania|TAS|Hobart|575,366

### Blocks

Code blocks without syntax highlighting:

```
var printText = $('.text').data('text');
var contentArray = printText.split('/n');
```

Code blocks with language specified for highlighting:

```js
var printText = $('.text').data('text');

var contentArray = printText.split('/n');
$.each(contentArray, function(index, newLine) {
  $('.text').append('<span style="display:block;" id="'+index+'"></span>');
  
  var lineID = index;
  var self = $(this);
    setTimeout(function () {
      $.each(self, function(index, chunk){
          setTimeout(function () {
            $('#'+lineID).append("<span>"+chunk+"</span>");
            $('body, html').scrollTop($(document).height());
          }, index*5);
      });
      
    }, index*100);
});
```

Block quotes: 

> Inspect anything brought into the house hopped up on goofballs give attitude flop over hide when guests come over chase mice lick butt behind the couch make muffins, attack feet flop over rub face on everything chew ipad power cord stand in front of the computer screen intrigued by the shower sweet beast under the bed why must they do that, intently sniff hand shake treat hunt anything that moves destroy couch sweet beast under the bed intently sniff hand intrigued by the shower chew ipad power cord.

## Equations

Inline equations work for simple expressions like $x^2$, but it's better to switch to display mode for more complex expressions. If I wanted to illustrate that a Maclaurin series expansion is a [Taylor series](https://en.wikipedia.org/wiki/Taylor_series) expansion of $f(x)$ around $x = 0$, I'd do this:

$$
f(0) + \frac{f^\prime(0)}{1!} x + \frac{f^{\prime\prime}(0)}{2!} x^2 + \frac{f^{\prime\prime\prime}(0)}{3!} x^3 + \ldots
$$
## Code

```{r}
(12 ^ 2) / 3.14
```

```{r}
#| message: false
library(stringr)
library(ggplot2)
library(tibble)
library(dplyr)

msg <- "hello cruel world"
msg |> 
  str_to_upper() |> 
  str_view("WORLD")
```

The litedown package defaults to `xfun::record_print()` for printing data frames and tibbles, which in turn uses `xfun::md_table()` to render the object as a markdown table. That produces results like this:

```{r}
starwars |> 
  select(name:homeworld, species) |> 
  filter(species == "Human")
```

You can specify your own print options to change this behaviour, or you can just call `print()` explicitly:

```{r}
starwars |> 
  select(name:homeworld, species) |> 
  filter(species == "Human") |> 
  print()
```


```{r}
#| label: footer
#| echo: false
#| results: asis
.blog$write_footer()
```

