---
title: Targets, litedown, and D&D spells
output:
  litedown::html_format:
    meta:
      css: "../_liteblog.css"
    options:
      toc: false
      js_highlight:
        package: prism
        style: tomorrow
---

In the dying days of 2024, a woman who should have been doing something useful like replaying the original Mass Effect trilogy for the n-th time instead decided to learn something about [litedown](https://yihui.org/litedown), [targets](https://books.ropensci.org/targets/), and [legendry](https://teunbrand.github.io/legendry/). This absurdity, which has absolutely no use case whatsoever and should be shunned by one and all, is the inevitable outcome of her poor decision making.

```{r}
#| label: post-listing
#| echo: false
#| results: "asis"
.blog <- readRDS("../_liteblog.rds")
.blog$write_post_list()
```

Should you have, in some drug-addled state no doubt, followed a capricious rabbit down some dark internet hold and ended up here by accident, your best bet is to close the browser and take a few deep breaths. You would be ill-advised to go to [blog.djnavarro.net](https://blog.djnavarro.net) to find other things I have written, and even more poorly-advised to point your browser at [djnavarro.net](https://djnavarro.net). 

The art at [art.djnavarro.net](https://art.djnavarro.net) is kind of neat though. 

```{r}
#| label: footer
#| echo: false
#| results: asis
.blog$write_footer()
```
